Results

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed tense

The cognitive effort expended also plays the most important role in the subsequent choice decision, which resembles previous findings of our group[@Scheffel2021]. 
Here, `r round((54/119)*100, digits = 1)` percent stated that they again chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)` percent stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)` percent stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in table XX in [supplementary material](#SupplementReasonChoice).

>>>>

The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
Here, `r round((54/119)*100, digits = 1)` percent stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)` percent stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)` percent stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in table XX in [supplementary material](#SupplementReasonChoice).
